---
title: "Full projections"
author: "Katy Gaythorpe"
date: "`r format(Sys.time(), '%d %B, %Y')`"
header-includes: 
- \usepackage{placeins}
output: 
  pdf_document:
    df_print: "kable"
params:
  save_samples: FALSE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, error = FALSE)
knitr::opts_chunk$set(
  fig.path = paste0("FullProjectionImagesRainfall", Sys.Date(), "/"),
  dpi = 300,
  dev = c('png')
)
```

# Introduction

We have estimated the temperature suitability parameters and GLM parameters separately. We now examine the results of estimating them together where the posterior of the parameters from both may be influenced by each other.

We start first with examining the convergence of the MCMC.

# MCMC diagnostics

Firstly, we are interested in whether the chains have converged to stable distribution and compare that distribution to the prior information.

```{r set_up}

library(maptools)
library(sp) 
library(shapefiles)
library(Hmisc)
library(fields)
library(dplyr)
library(EnvStats)
library(readr)
library(reshape)
library(abind)
library(mvtnorm)
library(RColorBrewer)
library(truncdist)
library(tibble)
library(magrittr)
library(pROC)

library(ggmcmc)
library(mcmcplots)
library(R.utils)

library(YFestimation)
library(snapalette)
library(KsetupR)

#########################################################################################################
### SETTING THE WORKING DIRECTORY ###
#########################################################################################################

shpdir = paste0("../","shapefiles/gadm2/")

#########################################################################################################
### LOADING SHAPEFILES AND COUNTRIES ###
#########################################################################################################

#read shapefiles in
shp0 = readShapePoly(paste0(shpdir, "Africa_adm0.shp")) #if gadm2
shp1 = readShapePoly(paste0(shpdir, "Africa_adm1.shp"))

#adjust titles
shp1$adm0_adm1 = paste(shp1$ISO, shp1$ID_1, sep="_")
shp1 = shp1[order(shp1$adm0_adm1),]

#read countries in
Countries = read_csv(paste0("../Data/","Countries.csv"))
c34 = Countries$c34
country34 = Countries$country34

#########################################################################################################
### SOURCE FUNCTIONS ###
#########################################################################################################

sourceDirectory("FUNCTIONS", modifiedOnly = FALSE)

#########################################################################################################
### LOAD ENVIRONMENTAL DATA ###
#########################################################################################################

Env_Table_path = paste0("../Data/","Environment/dat_worldclim_all_2019-04-15.csv")

dat_full = read.csv(Env_Table_path, 
                    stringsAsFactors = FALSE)

dat_full = prepare_climate_dat(dat_full, year = "now", scenario = NA)

temp_type = "worldclim_temp_mid"

modelVec = "cas.or.out~log.surv.qual.adm0+adm05+lon+logpop+temp_suitability+worldclim_temp_range+worldclim_rainfall" 
#########################################################################################################
### LOAD TEMPSUIT DATA ###
#########################################################################################################
### a
mordecai_biterate <- read_csv("Data/mordecai_biterate.csv")
hamlet_biterate = read_csv("Data/hamlet_biterate.csv")
mordecai_biterate$author = "mordecai"
hamlet_biterate$author = "hamlet"
names(hamlet_biterate) = names(mordecai_biterate)

dat_bite = rbind(mordecai_biterate, hamlet_biterate)

### mu
dat_mort <- read_csv("Data/Survival_mortality/SurvivalData_mordecai2018.csv")
dat_mort = filter(dat_mort, `Time (dpi)`>0)
dat_mort = filter(dat_mort, Alive+Dead+Censored>0)

### PDR
dat_EIP <- read_csv("Data/davis_EIP.csv")

### posterior samples
n_samples = 1000


```


```{r import_chains}


path =  get_latest_file(pattern = "GLM_tempsuit_MCMC_chain_") #"Z:/YF_climateChange/GLM_tempsuit_MCMC_chain_20190517" #


#get_chains
mcmc_out = get_chains(path, burnin = 2e6, thin = 1)

#mcmc_out %<>% filter(is.finite(posteriorProb))

plot(mcmc_out$posteriorProb, type = "l", ylab = "Posterior probability", xlab = "Iteration")# , ylim = c(-2e3, -1.8e3))

ind = which.max(mcmc_out$posteriorProb)

mcmc_out = mcmc_out[, 1:(ncol(mcmc_out)-2)]


```


```{r trace_basic_adm05, fig.height = 10, fig.width = 7}
par(mfrow = c(7,5), mar = c(2,4,2,1)+0.1)

for(i in 1:ncol(mcmc_out)){
  plot(mcmc_out[,i], type = "l", xlab = "", ylab = names(mcmc_out)[i])
}
```

```{r posterior, fig.height = 10, fig.width = 7}
chain_sub2 = convert.mcmc.list(mcmc_out)

chain_sub = ggs(chain_sub2 )

par(mfrow = c(7,5), mar = c(2,4,2,1)+0.1)
for(i in 1:ncol(mcmc_out)){
  plot(density(mcmc_out[,i]), 
       type = "l", xlab = "", main = names(mcmc_out)[i], col = "lightslateblue")
  polygon(density(mcmc_out[,i]), 
          type = "l", xlab = "", main = names(mcmc_out)[i], col = "lightslateblue", border = "slateblue")
}
```

```{r correlations, fig.height = 10, fig.width = 7}


ggs_crosscorrelation(chain_sub)

```

```{r caterpillar, fig.height = 10, fig.width = 7}

ggs_caterpillar(chain_sub)

### save values 
write.csv(ci(chain_sub), paste0("GLM_tempsuit_parameter_estimates_", 
                                format(Sys.time(),"%Y%m%d"), ".csv"), row.names = FALSE)

```

```{r running_mean}
ggs_running(chain_sub, family = "adm05GNB")

```

```{r partial}
ggs_compare_partial(chain_sub, family = "adm05GNB")

```

```{r raftery}
rd = coda::raftery.diag(chain_sub2)
rd[[1]]$resmatrix

max(rd[[1]]$resmatrix[,2])
```

# Plotting the fit

We do this first for the temperature suitability parameters and then for the GLM and temp suitability.

## Temperature suitability

```{r bite_rate_fit, fig.cap="Estimated bite rate (black) with bite rate data (red).", fig.height = 4, fig.width = 7}

dat_bite = dat_bite[order(dat_bite$T),]
plot(10:42, 
     briere(10:42, c(median(mcmc_out$a_T0), median(mcmc_out$a_Tm) ,median(mcmc_out$a_c )  )), 
     type = "l", ylim = c(0,3), lwd =1, 
     xlab = "Temperature", ylab = "Bite rate")

for (i in 1:n_samples){
  ind = sample(nrow(mcmc_out), 1)
  lines(10:42, briere(10:42, c(mcmc_out$a_T0[ind], mcmc_out$a_Tm[ind], mcmc_out$a_c[ind])), 
        col = rgb(0,0,0,alpha=0.01)  )
}
points(dat_bite$T, dat_bite$bite_rate, col = "red", pch =20)

```


```{r mortality_fit, fig.cap="Estimated mortality rate (black) with mortlity rate data (red)." , fig.height = 4, fig.width = 7}

Temp = 10:42

lf = quad(Temp, c(median(mcmc_out$mu_T0 ),median(mcmc_out$mu_Tm ), median(mcmc_out$mu_c )))
lf[lf<0] = 0
mu = ifelse( lf<=0, 1, 1/ lf ) +1e-8
plot(Temp, mu, xlab = "Temperature", ylab = "Mortality rate", type = "l", ylim = c(0,1))

for (i in 1:n_samples){
  ind = sample(nrow(mcmc_out), 1)
  lf = quad(Temp, c(mcmc_out$mu_T0[ind],
                    mcmc_out$mu_Tm[ind], 
                    mcmc_out$mu_c[ind]) )
  lf[lf<0] = 0
  mu = ifelse( lf<=0, 1, 1/ lf ) + 1e-8
  lines(Temp, mu, col = rgb(0,0,0,alpha=0.1))
}

points(dat_mort$Temp, dat_mort$Dead/(dat_mort$Dead+dat_mort$Alive), 
       pch = 20, col="red", cex = (dat_mort$Dead+dat_mort$Alive)/100)

```

```{r PDR_fit, fig.cap="Estimated PDR (black) with PDR data (red).", fig.height = 4, fig.width = 7}

plot(10:42, pmax( briere(10:42, c( median(mcmc_out$PDR_T0 ),
                                     median(mcmc_out$PDR_Tm ),
                                     median(mcmc_out$PDR_c ) ) ), 0), 
     type = "l", ylim = c(0,1), lwd =1, 
     xlab = "Temperature", ylab = "1 / Extrinsic incubation period")

for (i in 1:n_samples){
  ind = sample(nrow(mcmc_out), 1)
  lines(10:42, pmax( briere(10:42, c( mcmc_out$PDR_T0[ind] ,
                                        mcmc_out$PDR_Tm[ind] ,
                                        mcmc_out$PDR_c[ind] )  ), 0), 
        col = rgb(0,0,0,alpha=0.01)  )
}
points(dat_EIP$T, dat_EIP$PDR, col = "red", pch =20)

```

```{r temp_suit_fit, fig.cap="Estimated temperature index.", fig.height = 4, fig.width = 7}

Temp = seq(10, 42, by=0.01)

plot(Temp, temp_suitability(Temp ,apply(mcmc_out[,22:30], 2, median)), 
     ylim = c(0,100), type = "l", lwd =1, 
     xlab = "Temperature", ylab = "Suitability")

temp_suit_mat = NULL
for (i in 1:n_samples){
  ind = sample(nrow(mcmc_out), 1)
  t_s = temp_suitability(Temp ,  mcmc_out[ind,22:30] )
  
  lines(Temp, t_s, type = "l", ylim = c(0,1), lwd =1, 
        xlab = "Temperature", ylab = "Suitability", col = rgb(0,0,0,alpha=0.01)  )
  
  temp_suit_mat = rbind(temp_suit_mat, t_s )
}

colnames(temp_suit_mat) = Temp

peak = NULL
for (i  in 1:n_samples){
  peak = rbind(peak, as.numeric(names(which.max(temp_suit_mat[i,]))))
}

quantile(peak, c(0.025, 0.5, 0.975))
```

\FloatBarrier

## GLM fit (including temperature suitability)

We will map the median predictions and then examine uncertainty.

```{r plot_glm, fig.height=7, fig.width=10, fig.cap="Actual versus predicted probability of a yellow fever report for median posterior parameter estimates."}
snapal = "BudapestCitadel"



##################################################################################
### model ###

### TEMP SUITABILITY ###
dat_full_temp = cbind(dat_full,
                      temp_suitability(dat_full[,temp_type] , #mcmc_out[ind,22:30]))
                                       apply(mcmc_out[,22:30], 2 ,"median")) )
names(dat_full_temp)[ncol(dat_full_temp)] = "temp_suitability"

envdat = YFestimation::launch_env_dat(filepath = NA, dat_full= dat_full_temp , c34 = c34)  

### GET x ###

object_glm = fit_glm(dat =envdat$dat, depi = envdat$depi, modelVec ) 
x = object_glm[[2]]

### preds
Est_beta =  apply(mcmc_out[,1:21], 2, median) #as.numeric(mcmc_out[ind, 1:21])#


plot_glm_map(shp0, shp1, c34, envdat$dat, Est_beta, x, snapalette(snapal, 1000, type="continuous"))
```


```{r AUC}


### TEMP SUITABILITY ###
dat_full_temp = cbind(dat_full,
                      temp_suitability(dat_full[,temp_type] , #mcmc_out[ind,22:30]))
                                       apply(mcmc_out[,22:30], 2 ,"median")) )
names(dat_full_temp)[ncol(dat_full_temp)] = "temp_suitability"

envdat = YFestimation::launch_env_dat(filepath = NA, dat_full= dat_full_temp , c34 = c34)  

### GET x ###

object_glm = fit_glm(dat =envdat$dat, depi = envdat$depi, modelVec ) 
x = object_glm[[2]]

### preds
Est_beta =  apply(mcmc_out[,1:21], 2, median)

glmpreds = fun_calcPred( Est_beta ,x,type="response")

ROC_out = roc(response = envdat$dat$cas.or.out, predictor = glmpreds)

auc(ROC_out)

```

```{r plot_temp_suit, fig.height=10, fig.width=7, fig.cap = "Normalized temperature suitability from median of posterior predicted distribution."}
par(mar = 0*c(5.1,4.1,4.1,2.1))

temp_suit = (dat_full_temp$temp_suitability)
#temp_suit = dat_full_temp$worldclim_temp_mid

mybreaks= seq(0, max(temp_suit)+0.01, length.out=100)
mycols =   snapalette( "ST_art", length(mybreaks)-1, type = "continuous" )
vcols = findInterval(temp_suit,mybreaks)

mm = match(shp1$adm0_adm1, dat_full_temp$adm0_adm1)

plot(shp0, xlim=c(-15,50),ylim=c(-20,35))
mm0 = match(shp0$ISO,c34) #
#plot(shp0[is.na(mm0),],col="black",add=TRUE) 
plot(shp1[!is.na(mm),],col=mycols[vcols], xlim=c(-15,50), ylim=c(-20,35) , lty=0, add=TRUE)
plot(shp0,  add=TRUE)
#plot(shp0[is.na(mm0),],col="black",add=TRUE) 

image.plot(legend.only=TRUE,
           breaks=mybreaks,
           col=mycols,
           zlim=c(0,1), 
           horizontal = TRUE,
           legend.shrink = 0.75)

```


```{r glm_predict_uncertainty_prep, fig.height=10, fig.width=7, fig.cap="Coefficient of variation % for predictions."}

glm_pred_uncert = NULL

for(i in 1:n_samples){
  
  sample_ind = sample(nrow(mcmc_out), 1)
  
  ### TEMP SUITABILITY ###
  dat_full_temp = cbind(dat_full, temp_suitability(dat_full[,temp_type] , mcmc_out[sample_ind,22:30])  )
  names(dat_full_temp)[ncol(dat_full_temp)] = "temp_suitability"
  envdat = YFestimation::launch_env_dat(filepath = NA, dat_full = dat_full_temp, c34 = c34)  
  
  ### GET x ###
  
  object_glm = fit_glm(dat =envdat$dat, depi = envdat$depi, modelVec ) 
  x = object_glm[[2]]
  
  ### preds
  Est_beta =  as.numeric( mcmc_out[sample_ind,1:21] )
  glmpreds_tmp = fun_calcPred( Est_beta ,x,type="response")
  
  glm_pred_uncert = rbind(glm_pred_uncert, t(glmpreds_tmp) )
}
```

```{r glm_predict_uncertainty, fig.height=10, fig.width=7, fig.cap="Coefficient of variation % for predictions."}

par(mar = 0*c(5.1,4.1,4.1,2.1))

coeff_of_var = log10(apply(glm_pred_uncert, 2, sd )/apply(glm_pred_uncert, 2, mean ) * 100)

mybreaks = seq(min(coeff_of_var)-1,max(coeff_of_var)+1,length.out=100)
mycols =   snapalette( "EspiritoSanta", length(mybreaks)-1, type = "continuous" )
mm = match(shp1$adm0_adm1,envdat$dat$adm0_adm1)
vcols = findInterval(coeff_of_var,mybreaks)


plot(shp0, xlim=c(-15,45),ylim=c(-20,35))
mm0 = match(shp0$ISO,c34) #
plot(shp0[is.na(mm0),],col="black",add=T) 
plot(shp1[!is.na(mm),],col=mycols[vcols], xlim=c(-15,45), ylim=c(-20,35) , lty=0, add=T)
plot(shp0, xlim=c(-15,45),ylim=c(-20,35), add=T)

image.plot(legend.only=TRUE,breaks=mybreaks,col=mycols,zlim=c(0,1), horizontal = TRUE, 
           axis.args = list(at = c(-2:4), labels =c( "0.01","0.1","1", "10", "100","1,000","10,000"), las =2),
           legend.mar = 3.5)

```

# Transmission

We now use the estimated model to calculate the transmission intensity assuming the temperature is as fitted - see figure, and then assuming the temperature is increasing. We save the outputs in .csv to become inputs for thse next markdown document.

```{r setup_fit}

#########################################################################################################
### LOADING SEROLOGY DATA ###
#########################################################################################################

Serology = read.csv(paste0("../Data/","Serology/serology.csv"), stringsAsFactors = FALSE)
Serology = Serology %>% filter(country_zone != "CAF") # IGNORE CAF
seroout = process_serology(Serology)

#########################################################################################################
### POPULATION AND VACCINATION DATA ###
#########################################################################################################
path = "../Data/"

#function to collect , get totals for each year and proportions in each year
all_res_pop_3d = get_pop_data_3d(path = path, c_country=c34, dat=envdat$dat)

pop1 = all_res_pop_3d$pop1                                            #population import
pop3d = all_res_pop_3d$pop3d                                      #populations in 3d array
P_tot_2d = all_res_pop_3d$P_tot_2d                                    #total populations for each adm and year
p_prop_3d = all_res_pop_3d$p_prop_3d                                    #proportions of population

#get names
dim_adm  = dimnames(pop3d)[[1]]
dim_year = as.numeric(dimnames(pop3d)[[2]])
dim_age  = dimnames(pop3d)[[3]]

#########################################################################################################
### VACCINATION DATA ###
#########################################################################################################


vaccdir = paste0("../Data/", "Vaccination/")
# latest_vaccine_csv = "vaccination_coverage_by_adm1_year_age_base_skew0_update_2016-10-16.csv"
latest_vaccine_csv = "Outputs/adm1_old/vaccination_coverage_by_adm1_year_age_base_skew0.csv"   

vc2d = read.csv(paste0(vaccdir,latest_vaccine_csv), 
                stringsAsFactors = FALSE) 

names(vc2d)[names(vc2d)=="country"]= "adm0"                          #rename countries as adm0
names(vc2d)[names(vc2d)=="adm1"]= "adm0_adm1"                        #renames adm1 as adm0_adm1

# formally "repair_vc_data" from FOI model in Kevin's folder
for (colIndex in 3:ncol(vc2d)){                                      
  vc2d[,colIndex] = ifelse(is.na(vc2d[,colIndex]), vc2d[,colIndex-1], vc2d[,colIndex])
}
# restrict to lines in dat
vc2d = vc2d[vc2d[,"adm0_adm1"] %in% envdat$dat[,"adm0_adm1"],]

#vc3d
vc3d = transform_into_vc3d(vc2d,  adm="adm1")

# t0_vac_africa #
t0_vac_africa = calc_t0_vac_africa(vc3d)

# inc_v3d #
inc_v3d = calc_incidence_vac_general(vc3d)

# CALCULATE population moments #
pop_moments_whole = calc_pop_moments(p_prop_3d, 
                                     t0_vac_africa,
                                     dim_adm,
                                     dim_year,
                                     dim_age)
#########################################################################################################
### AGGREGATE POPULATION AND VACCINATION DATA ###
#########################################################################################################

#aggregate
list_aggregate_pop_vc =Make_aggregate_pop_vc_3d(pop1=pop1, 
                                                vc2d=vc2d, 
                                                sero_studies=seroout$sero_studies, 
                                                adm1s=seroout$adm1s)
pop_agg3d = list_aggregate_pop_vc$pop_agg3d
vc_agg3d = list_aggregate_pop_vc$vc_agg3d

#calculate aggregated incidence (same function as before)
inc_v3d_agg = calc_incidence_vac_general(vc_agg3d);dim(inc_v3d_agg)

#calculate aggregated moments (different fucntion before)
pop_moments_agg = calc_pop_moments_agg(pop_agg3d,
                                       seroout$t0_vac,
                                       dim_year,
                                       seroout$study_years)


#########################################################################################################
### CREATE R0 LOOKUP TABLE ###
#########################################################################################################

load(paste0("../YellowFeverModelEstimation2017/","R0_lookup_table.Rdata") )

#########################################################################################################
### pop at survey ###
#########################################################################################################
#foi_const_surv = c(0,1e-6,0,0,0,0,rep(0,no_sero_surveys-6))
foi_const_surv = rep(0, seroout$no_sero_surveys)

list_pop_at_survey = create_pop_at_survey(pop_agg3d, 
                                          seroout$sero_studies,
                                          dim_year)
p_at_survey = list_pop_at_survey$p_at_survey_3d
P_tot_survey = list_pop_at_survey$P_tot_survey_2d

```

```{r import_serology_fit}

filepath = "Z:/MultiModelInference/multi_model_MCMC_chain_20180622" 


mcmc_out_sero = get_chains(filepath, burnin = 1, thin = 100)

```



```{r transmission, fig.height=10, fig.width=7, fig.cap="Force of infection, %.", echo=TRUE}

### TEMP SUITABILITY ###
dat_full_temp = cbind(dat_full,
                      temp_suitability(dat_full[,temp_type] , #mcmc_out[ind,22:30]))
                                       apply(mcmc_out[,22:30], 2 ,"median")) )
names(dat_full_temp)[ncol(dat_full_temp)] = "temp_suitability"

envdat = YFestimation::launch_env_dat(filepath = NA, dat_full= dat_full_temp , c34 = c34)  

### GET x ###

object_glm = fit_glm(dat =envdat$dat, depi = envdat$depi, modelVec ) 
x = object_glm[[2]]


ii= 2:22

varsin_nc=ii[-grep("adm0",colnames(x))] - 1 

mcmc_out_f = filter(mcmc_out_sero, model_chain == 0)

adjusted_params = c(exp(median(mcmc_out_f[,1])), 
                    apply(mcmc_out[,1:21], 2, median, na.rm = T), # as.numeric(mcmc_out[ind,1:21]), #
                    exp(apply(mcmc_out_f[,c(2:41)], 2, median, na.rm = T)),
                    exp(median(mcmc_out_f[,ncol(mcmc_out_f)])) )

names(adjusted_params)[c(1,length(adjusted_params))] = c("vac_eff", "vc_factor_CMRs")


colours = (snapalette("Camden", 100, type = "continuous"))


runs = YFestimation::fun_calc_transmission_Africa(x,
                                                  ii ,
                                                  seroout ,
                                                  params = adjusted_params ,
                                                  dat = envdat$dat ,
                                                  t0_vac_africa ,
                                                  dim_year ,
                                                  dim_age ,
                                                  p_prop_3d ,
                                                  P_tot_2d ,
                                                  inc_v3d ,
                                                  pop1,
                                                  vc2d,
                                                  varsin_nc,
                                                  polydeg = 5,
                                                  R0_lookup,
                                                  model_type = "Foi")
names(runs) = envdat$dat$adm0_adm1

mybreaks= seq(-3, 1, length.out=101)
mm = match(shp1$adm0_adm1,envdat$dat$adm0_adm1)
vcols = findInterval(log10(runs*100),mybreaks)

plot(shp0, xlim=c(-15,45),ylim=c(-20,30))
mm0 = match(shp0$ISO,Countries$c34) #
plot(shp0[is.na(mm0),],col="black",add=T)
plot(shp1[!is.na(mm),],col=colours[vcols], xlim=c(-15,45),ylim=c(-20,30) , lty=0, add=T)

plot(shp0, lwd=2, add=T)


image.plot(legend.only=TRUE, breaks=mybreaks, col=colours, zlim=c(0,1), horizontal = TRUE,
           axis.args = list(at = c(-3:1), labels =c("0.001", "0.01", "0.1", "1", "10"), las =2),
           legend.mar = 3.5)


```


