---
title: "Full projections"
author: "Katy Gaythorpe"
date: "`r format(Sys.time(), '%d %B, %Y')`"
header-includes: 
- \usepackage{placeins}
output: 
  pdf_document:
    df_print: "kable"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, error = FALSE)
knitr::opts_chunk$set(
  fig.path = "FullProjectionImages/",
  dpi = 300
)
```

# Introduction

We have estimated the temperature suitability parameters and GLM parameters separately. We now examine the results of estimating them together where the posterior of the parameters from both may be influenced by each other.

We start first with examining the convergence of the MCMC.

# MCMC diagnostics

Firstly, we are interested in whether the chains have converged to stable distribution and compare that distribution to the prior information.

```{r set_up}

library(maptools)
library(sp) 
library(shapefiles)
library(Hmisc)
library(fields)
library(dplyr)
library(EnvStats)
library(readr)
library(reshape)
library(abind)
library(mvtnorm)
library(RColorBrewer)
library(truncdist)
library(wesanderson)
library(ggmcmc)
library(mcmcplots)

#########################################################################################################
### SETTING THE WORKING DIRECTORY ###
#########################################################################################################

shpdir = paste0("../","shapefiles/gadm2/")

#########################################################################################################
### LOADING SHAPEFILES AND COUNTRIES ###
#########################################################################################################

#read shapefiles in
shp0 = readShapePoly(paste0(shpdir, "Africa_adm0.shp")) #if gadm2
shp1 = readShapePoly(paste0(shpdir, "Africa_adm1.shp"))

#adjust titles
shp1$adm0_adm1 = paste(shp1$ISO, shp1$ID_1, sep="_")
shp1 = shp1[order(shp1$adm0_adm1),]

#read countries in
Countries = read_csv(paste0("../Data/","Countries.csv"))
c34 = Countries$c34
country34 = Countries$country34

#########################################################################################################
### SOURCE FUNCTIONS ###
#########################################################################################################

R.utils::sourceDirectory("FUNCTIONS/FUNCTIONS_combined", modifiedOnly = FALSE)
source("FUNCTIONS/GLMonly_functions.R")

#########################################################################################################
### LOAD ENVIRONMENTAL DATA ###
#########################################################################################################

Env_Table_path = (paste0("../Data/","Environment/Africa_adm1_dat_2017.csv")) #this file is adapted by hand to have latest outbreaks

dat_full = read.csv(Env_Table_path, stringsAsFactors=F)

#########################################################################################################
### LOAD TEMPSUIT DATA ###
#########################################################################################################
### a
mordecai_biterate <- read_csv("Data/mordecai_biterate.csv")
hamlet_biterate = read_csv("Data/hamlet_biterate.csv")
mordecai_biterate$author = "mordecai"
hamlet_biterate$author = "hamlet"
names(hamlet_biterate) = names(mordecai_biterate)

dat_bite = rbind(mordecai_biterate, hamlet_biterate)

### mu
dat_mort <- read_csv("Data/Survival_mortality/SurvivalData_mordecai2018.csv")
dat_mort = filter(dat_mort, `Time (dpi)`>0)
dat_mort = filter(dat_mort, Alive+Dead+Censored>0)

### PDR
dat_EIP <- read_csv("Data/davis_EIP.csv")

### posterior samples
n_samples = 1000

```


```{r import_chains}

setwd("GLM_tempsuit_MCMC_chain_20180823_hamlet")

temp = list.files(pattern="\\.csv$")

fi = file.info(temp)
temp = temp[fi$size>5000]

l=lapply(temp,read.csv)
for(i in 1:length(l)){l[[i]] = l[[i]][,-1]}

mcmc_out=data.table::rbindlist( l )

mcmc_out = as.data.frame( mcmc_out[80000:nrow(mcmc_out),1:28] )

```


```{r trace_basic, fig.height = 10, fig.width = 7}

par(mfrow = c(7,4), mar = c(2,4,2,1)+0.1)
for(i in 1:ncol(mcmc_out)){
  plot(mcmc_out[,i], type = "l", xlab = "", ylab = names(mcmc_out)[i])
}
```

```{r posterior, fig.height = 10, fig.width = 7}
par(mfrow = c(7,4), mar = c(2,4,2,1)+0.1)
for(i in 1:ncol(mcmc_out)){
  plot(density(mcmc_out[,i]), type = "l", xlab = "", main = names(mcmc_out)[i], col = "lightslateblue")
  polygon(density(mcmc_out[,i]), type = "l", xlab = "", main = names(mcmc_out)[i], col = "lightslateblue", border = "slateblue")
}
```

```{r correlations, fig.height = 10, fig.width = 7}
chain_sub2 = convert.mcmc.list(mcmc_out)

chain_sub = ggs(chain_sub2 )

ggs_crosscorrelation(chain_sub)

```

```{r caterpillar, fig.height = 10, fig.width = 7}

ggs_caterpillar(chain_sub)


### save values 
write.csv(ci(chain_sub), "GLM_tempsuit_parameter_estimates.csv", row.names = FALSE)

```


# Plotting the fit

We do this first for the temperature suitability parameters and then for the GLM and temp suitability.

## Temperature suitability

```{r bite_rate_fit, fig.cap="Estimated bite rate (black) with bite rate data (red).", fig.height = 4, fig.width = 7}

dat_bite = dat_bite[order(dat_bite$T),]
plot(dat_bite$T, briere(dat_bite$T, T0 =  median(mcmc_out$a_T0 ),
                    Tm =  median(mcmc_out$a_Tm ),
                    c =  median(mcmc_out$a_c )  ), type = "l", ylim = c(0,3), lwd =1, 
     xlab = "Temperature", ylab = "Bite rate")

for (i in 1:n_samples){
lines(dat_bite$T, briere(dat_bite$T, T0 = mcmc_out$a_T0[sample(nrow(mcmc_out), 1)] ,
                           Tm =  mcmc_out$a_Tm[sample(nrow(mcmc_out), 1)] ,
                            c =  mcmc_out$a_c[sample(nrow(mcmc_out), 1)]   ), col = rgb(0,0,0,alpha=0.01)  )
}
points(dat_bite$T, dat_bite$bite_rate, col = "red", pch =20)

```


```{r mortality_fit, fig.cap="Estimated mortality rate (black) with mortlity rate data (red)." , fig.height = 4, fig.width = 7}

Temp = unique(dat_mort$Temp)

lf = quad(Temp, median(mcmc_out$mu_T0 ),median(mcmc_out$mu_Tm ), median(mcmc_out$mu_c ))
lf[lf<0] = 0
mu = ifelse( lf<=0, 1, 1/ lf ) +1e-8
plot(Temp, mu, xlab = "Temperature", ylab = "Mortality rate", type = "l", ylim = c(0,1))

for (i in 1:n_samples){
  lf = quad(Temp, mcmc_out$mu_T0[sample(nrow(mcmc_out), 1)],
            mcmc_out$mu_Tm[sample(nrow(mcmc_out), 1)], 
            mcmc_out$mu_c[sample(nrow(mcmc_out), 1)] )
lf[lf<0] = 0
mu = ifelse( lf<=0, 1, 1/ lf ) + 1e-8
lines(Temp, mu, col = rgb(0,0,0,alpha=0.1))
}

points(dat_mort$Temp, dat_mort$Dead/(dat_mort$Dead+dat_mort$Alive), pch = 20, col="red", cex = (dat_mort$Dead+dat_mort$Alive)/100)

```

```{r PDR_fit, fig.cap="Estimated PDR (black) with PDR data (red).", fig.height = 4, fig.width = 7}

plot(dat_EIP$T, briere(dat_EIP$T, T0 =  median(mcmc_out$a_T0 ),
                    Tm =  median(mcmc_out$a_Tm ),
                    c =  median(mcmc_out$a_c )  ), type = "l", ylim = c(0,1), lwd =1, 
     xlab = "Temperature", ylab = "PDR")

for (i in 1:n_samples){
lines(dat_EIP$T, briere(dat_EIP$T, T0 = mcmc_out$a_T0[sample(nrow(mcmc_out), 1)] ,
                           Tm =  mcmc_out$a_Tm[sample(nrow(mcmc_out), 1)] ,
                            c =  mcmc_out$a_c[sample(nrow(mcmc_out), 1)]   ), col = rgb(0,0,0,alpha=0.01)  )
}
points(dat_EIP$T, dat_EIP$PDR, col = "red", pch =20)

```

```{r temp_suit_fit, fig.cap="Estimated temperature index.", fig.height = 4, fig.width = 7}

Temp = 15:42

plot(Temp, temp_suitability(Temp ,apply(mcmc_out[,20:28], 2, median)), ylim = c(0,30), type = "l", lwd =1, 
     xlab = "Temperature", ylab = "Suitability")

for (i in 1:n_samples){
lines(Temp, temp_suitability(Temp , as.numeric( mcmc_out[sample(nrow(mcmc_out), 1),20:28]) ), type = "l", ylim = c(0,1), lwd =1, 
     xlab = "Temperature", ylab = "Suitability", col = rgb(0,0,0,alpha=0.01)  )
}


```

\FloatBarrier

## GLM fit (including temperature suitability)

We will map the median predictions and then examine uncertainty.

```{r plot_glm, fig.height=10, fig.width=7, fig.cap="Actual versus predicted probability of a yellow fever report for median posterior parameter estimates."}

par(mfrow=c(2,1), mar = c(3,3,1,0)+0.1)

### data ###
plot(shp0, xlim=c(-15,45),ylim=c(-20,35), main = "Location of YF reports")
mm0 = match(shp0$ISO,c34) #
plot(shp0[is.na(mm0),],col="black",add=T)

pres= dat_full$adm0_adm1[dat_full$cas.or.out>0]
mm1<-match(shp1$adm0_adm1,pres)
mm1<-match(pres, shp1$adm0_adm1)


plot(shp1[mm1,],col="red", add=T)
plot(shp0,lwd=2, add=T)
plot(shp1,lwd=1, add=T)

##################################################################################
### model ###

### TEMP SUITABILITY ###
dat_full_temp = cbind(dat_full, temp_suitability(dat_full[,"ERAday.mean"] , apply(mcmc_out[,20:28], 2 ,"median")) )
names(dat_full_temp)[ncol(dat_full_temp)] = "temp_suitability"
envdat = launch_env_dat(dat_full_temp,c34)  

### GET x ###
modelVec = "cas.or.out~log.surv.qual.adm0+adm05+lon+logpop+temp_suitability" 
object_glm = fit_glm(dat =envdat$dat, depi = envdat$depi, modelVec ) 
x = object_glm[[2]]

### preds
Est_beta =  apply(mcmc_out[,1:19], 2, median)
glmpreds_tmp = fun_calcPred( Est_beta ,x,type="response")

mybreaks = seq(0,1.0001,by=0.01)
mycols =  heat.colors(length(mybreaks)-1)
mm = match(shp1$adm0_adm1,envdat$dat$adm0_adm1)
vcols = findInterval(glmpreds_tmp,mybreaks)
vcols=101-vcols

plot(shp0, xlim=c(-15,45),ylim=c(-20,35), main="as fitted")
mm0 = match(shp0$ISO,c34) #
plot(shp0[is.na(mm0),],col="black",add=T) 
plot(shp1[!is.na(mm),],col=mycols[vcols], xlim=c(-15,45),ylim=c(-20,30) , lty=0, add=T)
plot(shp0, xlim=c(-15,45),ylim=c(-20,35), add=T)

```


```{r glm_predict_uncertainty, fig.cap="Coefficient of variation % for predictions."}

glm_pred_uncert = NULL

for(i in 1:n_samples){
  
  sample_ind = sample(nrow(mcmc_out), 1)
  
  ### TEMP SUITABILITY ###
  dat_full_temp = cbind(dat_full, temp_suitability(dat_full[,"ERAday.mean"] , as.numeric(mcmc_out[sample_ind,20:28]) ) )
  names(dat_full_temp)[ncol(dat_full_temp)] = "temp_suitability"
  envdat = launch_env_dat(dat_full_temp,c34)  
  
  ### GET x ###
  modelVec = "cas.or.out~log.surv.qual.adm0+adm05+lon+logpop+temp_suitability" 
  object_glm = fit_glm(dat =envdat$dat, depi = envdat$depi, modelVec ) 
  x = object_glm[[2]]
  
  ### preds
  Est_beta =  as.numeric( mcmc_out[sample_ind,1:19] )
  glmpreds_tmp = fun_calcPred( Est_beta ,x,type="response")
  
  glm_pred_uncert = rbind(glm_pred_uncert, t(glmpreds_tmp) )
}

coeff_of_var = log10(apply(glm_pred_uncert, 2, sd )/apply(glm_pred_uncert, 2, mean ) * 100)

mybreaks = seq(min(coeff_of_var)-1,max(coeff_of_var)+1,length.out=100)
mycols =  rev( colorRampPalette(brewer.pal(11, "PuOr") )(length(mybreaks)-1) )
mm = match(shp1$adm0_adm1,envdat$dat$adm0_adm1)
vcols = findInterval(coeff_of_var,mybreaks)


plot(shp0, xlim=c(-15,45),ylim=c(-20,35), main="")
mm0 = match(shp0$ISO,c34) #
plot(shp0[is.na(mm0),],col="black",add=T) 
plot(shp1[!is.na(mm),],col=mycols[vcols], xlim=c(-15,45),ylim=c(-20,30) , lty=0, add=T)
plot(shp0, xlim=c(-15,45),ylim=c(-20,35), add=T)

image.plot(legend.only=TRUE,breaks=mybreaks,col=mycols,zlim=c(0,1), horizontal = TRUE, 
                    axis.args = list(at = c(-2:4), labels =c( "0.01","0.1","1", "10", "100","1,000","10,000"), las =2),
                    legend.mar = 3.5)

```

# Predictions

We now use the estimated model to create predictions of the change in burden given changes in temperature.

```{r setup_fit}
#########################################################################################################
### SOURCE FUNCTIONS ###
#########################################################################################################

source("../MultiModelInference/FUNCTIONS/Functions_Foi_model_reestimation.R") 
source("../MultiModelInference/FUNCTIONS/Functions_R0_model_reestimation.R") 
source("../MultiModelInference/FUNCTIONS/MCMC_functions.R") 
source("../MultiModelInference/FUNCTIONS/ProductSpaceFunctions.R") 
source("../MultiModelInference/FUNCTIONS/ProductSpaceFunctions_Sero.R")

#########################################################################################################
### LOADING SEROLOGY DATA ###
#########################################################################################################

#read serology in
Serology = read_csv(paste0("../Data/","Serology/serology.csv"))
Serology = filter(Serology, country_zone != "TCD_zone2") #ignoring this because there are no samples

### turn off some entries
Serology = filter(Serology, country_zone != "CAF")

#extracting values as the file is read as a tibble
sero_studies =  unique(Serology$country_zone)                                      #serology locations                                                      

#minimum of sero survey age groups
study_years = pull( unique(Serology[,c("country_zone","year") ] )[ ,2] , year)     #years each survey occurred
no_sero_surveys = length(sero_studies)                                             #Number of sero surveys in database

no_age_groups = rep(0,no_sero_surveys)                                             #Number of age groups in each survey
for (surveyIndex in 1:no_sero_surveys){
  no_age_groups[surveyIndex] = nrow( filter(Serology, country_zone== sero_studies[surveyIndex]) ) 
}

vc_factor = pull(unique(Serology[,c("country_zone","vc_factor") ] )[ ,2], vc_factor)  #whether to account for vaccination in serology or not
t0_vac = pull(unique(Serology[,c("country_zone","t0_vac") ] )[ ,2]  , t0_vac)         #first incidence of vaccination, pulled from tibble
names(t0_vac)=pull(unique(Serology[,c("country_zone","t0_vac") ] )[ ,1]  , country_zone)

adm1s_tibble = unique(Serology[ , c("country_zone", "gadm2")])[ ,2]                   #shape file admin locations in tibble form
adm1s=list()
for (surveyIndex in 1:no_sero_surveys) {
  adm1s[surveyIndex] = strsplit(as.character(adm1s_tibble[surveyIndex,1]),",")
}


#########################################################################################################
### POPULATION AND VACCINATION DATA ###
#########################################################################################################
path = "../Data/"

#function to collect , get totals for each year and proportions in each year
all_res_pop_3d = get_pop_data_3d(path = path, c_country=c34, dat=dat)

pop1 = all_res_pop_3d$pop1                                            #population import
pop3d = all_res_pop_3d$pop3d                                      #populations in 3d array
P_tot_2d = all_res_pop_3d$P_tot_2d                                    #total populations for each adm and year
p_prop_3d = all_res_pop_3d$p_prop_3d                                    #proportions of population

#get names
dim_adm  = dimnames(pop3d)[[1]]
dim_year = as.numeric(dimnames(pop3d)[[2]])
dim_age  = dimnames(pop3d)[[3]]
dim_survey = sero_studies

#########################################################################################################
### VACCINATION DATA ###
#########################################################################################################

vaccdir = paste0("../Data/", "Vaccination/")
# latest_vaccine_csv = "vaccination_coverage_by_adm1_year_age_base_skew0_update_2016-10-16.csv"
latest_vaccine_csv = "Outputs/adm1_old/vaccination_coverage_by_adm1_year_age_base_skew0.csv"   #updated at end of 2017

vc2d = read.csv(paste0(vaccdir,latest_vaccine_csv),stringsAsFactors = F, h=T) #read in latest vaccine coverage estimates

names(vc2d)[names(vc2d)=="country"]= "adm0"                          #rename countries as adm0
names(vc2d)[names(vc2d)=="adm1"]= "adm0_adm1"                        #renames adm1 as adm0_adm1

# formally "repair_vc_data" from FOI model in Kevin's folder
for (colIndex in 3:ncol(vc2d)){                                      #before 1995, we have NA values for those aged >75
  vc2d[,colIndex] = ifelse(is.na(vc2d[,colIndex]), vc2d[,colIndex-1], vc2d[,colIndex])
}
# restrict to lines in dat
vc2d = vc2d[vc2d[,"adm0_adm1"] %in% dat[,"adm0_adm1"],]

# create 3d array of adm, year, age
vc3d = transform_into_vc3d(vc2d,  adm="adm1")

#########################################################################################################
### CALCULATE VACCINE INCIDENCE ###
#########################################################################################################
inc_v3d = calc_incidence_vac_general(vc3d)

#########################################################################################################
### CALCULATE t0_vac_Africa ###
#########################################################################################################
t0_vac_africa = calc_t0_vac_africa(vc3d)

#########################################################################################################
### CALCULATE population moments ###
#########################################################################################################
pop_moments_whole = calc_pop_moments(p_prop_3d, t0_vac_africa,dim_adm,dim_year,dim_age)
#remember the last year of the data is hard-coded into this function so as the data gets updated, this should be checked

#########################################################################################################
### AGGREGATE POPULATION AND VACCINATION DATA ###
#########################################################################################################

#aggregate
list_aggregate_pop_vc =Make_aggregate_pop_vc_3d(pop1=pop1, vc2d=vc2d, sero_studies=sero_studies, adm1s=adm1s)
pop_agg3d = list_aggregate_pop_vc$pop_agg3d
vc_agg3d = list_aggregate_pop_vc$vc_agg3d

#calculate aggregated incidence (same function as before)
inc_v3d_agg = calc_incidence_vac_general(vc_agg3d);dim(inc_v3d_agg)

#calculate aggregated moments (different fucntion before)
pop_moments_agg = calc_pop_moments_agg(pop_agg3d,t0_vac,dim_year,study_years); dim(pop_moments_agg)


#########################################################################################################
### CREATE R0 LOOKUP TABLE ###
#########################################################################################################

load(paste0("../MultiModelInference/","R0_lookup_table.Rdata") )

#########################################################################################################
### pop at survey ###
#########################################################################################################
#foi_const_surv = c(0,1e-6,0,0,0,0,rep(0,no_sero_surveys-6))
foi_const_surv = rep(0, no_sero_surveys)

list_pop_at_survey = create_pop_at_survey(pop_agg3d,dim_survey,dim_year)
p_at_survey = list_pop_at_survey$p_at_survey_3d
P_tot_survey = list_pop_at_survey$P_tot_survey_2d

```